---
title: "Introduction to K-NN Algorithm"
author: "Heaven Klair"
date: "5/7/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the dataset

```{r, echo=TRUE}
dataset = read.csv('Social_Network_Ads.csv')
dataset = dataset[1:3]   #Only take the necessary variables from the dataset
dataset
```

## Encoding the target feature as a factor

```{r, echo=TRUE}
dataset$Purchased = factor(dataset$Purchased, levels = c(0,1))
```

## Splitting the dataset into the Training and Test set

```{r, echo=TRUE}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Purchased, SplitRatio = 0.75)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```

## Feature Scaling

Scale the appropriate variables.
```{r, echo=TRUE}
training_set[, -3] = scale(training_set[, -3])
test_set[, -3] = scale(test_set[, -3])
```

## Fitting K-NN to the training set and and Predicting the Test Set Results

```{r, echo=TRUE}
#Create your own classifier here. Below is just an example.

library(class)

y_pred = knn(train = training_set[, -3], 
             test = test_set[, -3],
             cl = training_set[, 3],
             k = 5)
y_pred
```

The library to selected K-NN package is called "class".

The Model for knn is as follows:

knn(train, test, cl, k = 1, l = 0, prob = FALSE, use.all = TRUE)

train: matrix or data frame of training set cases.

test: matrix or data frame of test set cases. A vector will be interpreted as a row vector for a single case.

cl: factor of true classifications of training set. The training and test set above are the independent variables, and we need a place to include the information about dependent variables (categorical dependent variable). So "cl" is where we do it.

The output of y_pred are the 100 predictions that K-NN produced.

Look at the dataset and see the first five customers. We see that they did not buy the SUV. Now we look at the predicted results from K-NN, and notice that the algorithm predicted the results correctly (the first five predictions are 0's).

## Making the Confusion Matrix

Confusion Matrix will help us calculate the number of correct and incorrect predictions.
```{r, echo=TRUE}
cm = table(test_set[,  3], y_pred)
cm
```

We focus on (1,1) and (2,2) elements in the matrix. These two elements are the number of correct predictions. The elements (1,2) and (2,1) are the incorrect predictions.


## Visualizing the Training set results

```{r, echo=TRUE}
library(ggplot2)
set = training_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('Age', 'EstimatedSalary')
y_grid = knn(train = training_set[, -3], 
               test = grid_set,
               cl = training_set[, 3],
               k = 5)

plot(set[, -3],
     main = 'Classifier (Training set)',
     xlab = 'Age', ylab = 'Estimated Salary',
     xlim = range(X1), ylim = range(X2)) +
  contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE) +
  points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'springgreen3', 'tomato')) +
  points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'green4', 'red3'))
```



# Visualizing the Test set results
```{r, echo=TRUE}
#library(ElemStatLearn)
set = test_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('Age', 'EstimatedSalary')
y_grid = knn(train = training_set[, -3], 
               test = grid_set,
               cl = training_set[, 3],
               k = 5)
plot(set[, -3], main = 'Classifier (Test set)',
     xlab = 'Age', ylab = 'Estimated Salary',
     xlim = range(X1), ylim = range(X2)) + 
  contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE) + 
  points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'springgreen3', 'tomato')) +
  points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'green4', 'red3'))
```


