---
title: "Multiple Linear Regression (part 2)"
author: "Heaven Klair"
date: "5/7/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Dataset
```{r, echo = TRUE}
mouse.data <- data.frame(
  size = c(1.4,2.6,1.0,3.7,5.5,3.2,3.0,4.9,6.3),
  weight = c(0.2,1.8,2.4,3.5,3.9,4.4,5.1,5.6,6.3),
  tail = c(0.7,1.3,0.7,2.0,3.6,3.0,2.9,3.9,4.0)
)
mouse.data

```

## Plot the data

```{r, echo = TRUE}
plot(mouse.data$weight, mouse.data$size)
```

We can see a relationship between the weight and the size, so lets do regression to find out.

## Simple Linear Regression
```{r, echo = TRUE}
simple.regressor = lm(size ~ weight,
               data = mouse.data)

print(summary(simple.regressor))
```

The most important value are at the bottom of the summary function: Adjusted R-squared, and p-value. Both of them together tells us that weight does a good job in predicting the size of the mouse.

## Adding least squares fit line to the graph
```{r, echo = TRUE}
plot(mouse.data$weight, mouse.data$size) +
  abline(simple.regressor, col = "red", lwd=2)
```

## Multiple Linear Regression

Now we will use weight and tail to predict size.

## Plot the data

```{r, echo = TRUE}
plot(mouse.data)
```

## Multiple Linear Regression
```{r, echo = TRUE}
multiple.regressor = lm(size ~ .,
               data = mouse.data)

print(summary(multiple.regressor))
```

Now we are interested in the Adjusted $R^2$ value. In Multiple Regression, the Coefficients section is more important. The weight row compares the multiple regression to the simple regression. The p-value for weight is 0.4837. It means that using weight and tail isn't significantly better than using tail alone to predict size.

The p-value for tail is 0.0216. It means using weight and tail is significantly better than using weight along to predict size. In summary (in the end), the p-value is 0.003628. It means that using weight and tail to predict size is a good. But if we wanted to save time, we could spare ourselves the agony of weighting mice and just use their tail length to predict size.