---
title: "Regression Template"
author: "Heaven Klair"
date: "4/4/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Regression Template
This regression Template is very useful for the next non-linear Regression models like SVR, decision tree and random forest, etc.

## Importing the dataset
```{r, echo=TRUE}
dataset = read.csv('Position_Salaries.csv')
dataset = dataset[2:3]
```


## Splitting the dataset into the Training and Test set
There is no need to split the dataset into training set and test set for the Position_Salaries csv file because the dataset is pretty small, and we want to get as much values as we can for the training purpose. 

If the dataset is large enough, below is the template for splitting the dataset into training and test set.

```{r, echo=TRUE}
# install.packages('caTools')
# library(caTools)
# set.seed(123)
# split = sample.split(dataset$DependentVariable, SplitRatio = 0.8)
# training_set = subset(dataset, split == TRUE)
# test_set = subset(dataset, split == FALSE)
```


## Feature Scaling
Since, we did not create a Training or Test set, we do not need to do feature scaling. However a template to feature scale the dataset is below
```{r, echo=TRUE}
#training_set = scale(training_set)
#test_set = scale(test_set)
```


## Fitting Regression Model to the Dataset
```{r, echo=TRUE}
# Create your regressor here
```

## Predicting a new result with Regression Model
```{r, echo=TRUE}
y_pred = predict(regressor, data.frame(Level = 6.5))
```

## Visualising the Regression Results
```{r, echo=TRUE}
library(ggplot2)
ggplot() + 
  geom_point(aes(x = dataset$Level, y = dataset$Salary),
             colour = 'red') +
  geom_line(aes(x = dataset$Level, y = predict(regressor, newdata = dataset )),
             colour = 'blue') +
  ggtitle('Truth or Bluff (Linear Regression)') +
  xlab('Level') +
  ylab('Salary')
```

## Visualising the Regression Model Results (Higher Resolution)
```{r, echo=TRUE}
library(ggplot2)
x_grid = seq(min(dataset$Level), max(dataset$Level), 0.1)

ggplot() + 
  geom_point(aes(x = dataset$Level, y = dataset$Salary),
             colour = 'red') +
  geom_line( aes( x = x_grid, y = predict(regressor, newdata = data.frame( Level = x_grid ))),
             colour = 'blue') +
  ggtitle('Regression Model') +
  xlab('X Label') +
  ylab('Y Label')
```
"x_grid = seq(min(dataset$Level), max(dataset$Level), 0.1)" creates a 90 level grid with an increment of 0.1. This is done so that we can have more values to plot the graph, and have a smoother curve.

In "geom_line":
1. "x = dataset$Levels" changed to "x = x_grid": because x_grid is our new values of x.
2.  "newdata = dataset" changed to "newdata = data.frame(Level = x_grid ))": Because we want to make prediction based on the new values, which are not in the dataset. Since the "newdata" argument is expecting a dataframe, so we need to declare a dataframe first. Intutively, we need to make dataframe of x_grid. Since we would like to create dataframe of new "Levels", we will need to specify "Levels". By doing "data.frame(Level = x_grid )" we are creating a new column of levels containing all the levels in the sequence x_grid here.



