---
title: "Introduction to Naive Bayes (Udemy)"
author: "Heaven Klair"
date: "6/15/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Introduction to Naive Bayes (Udemy Course)"
author: "Heaven Klair"
date: "6/6/2022"
output: pdf_document
---

## Importing the dataset


```{r, echo=TRUE}
dataset = read.csv('Social_Network_Ads.csv')
Age = dataset$Age
EstimatedSalary = dataset$EstimatedSalary
Purchased = dataset$Purchased
```

## Splitting the dataset into the Training set and Test set

You can also embed plots, for example:

```{r, echo=TRUE}
library(caTools)
set.seed(123)
split = sample.split(dataset$Purchased, SplitRatio = 0.75)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```


## Feature Scaling

```{r, echo=TRUE}
training_set[-3] = scale(training_set[-3])
test_set[-3] = scale(test_set[-3])
```

## Fitting classifier to the Training set

```{r, echo=TRUE}
library(e1071)
classifier = naiveBayes(x = training_set[-3],
                        y = training_set$Purchased)
```

## Predicting the Test set results

```{r, echo=TRUE}
y_pred = predict(classifier, newdata = test_set[-3])
```

## Making the Confusion Matrix

```{r, echo=TRUE}
cm = table(test_set[, 3], y_pred)
cm
```




## Visualising the Training set results

```{r, echo=TRUE}
#
```

```{r, echo=TRUE}
# install.packages('tidyverse')
library(tidyverse)
# expand.grid('Age' = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01),
# 'EstimatedSalary' = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01))%>% mutate(prob_set=predict(classifier, type = 'response', newdata = .),
# y_grid = ifelse(prob_set > 0.5, 1, 0))%>%
# ggplot() +
# geom_point(aes(x=Age, y=EstimatedSalary, color=y_grid)) +
# geom_point(data=training_set, aes(x=Age, y=EstimatedSalary,colour=as.numeric(Purchased)))
```



## Visualising the Test set results

```{r, echo=TRUE}

```

